\documentclass[a4paper,twocolumn,twoside,notitlepage,10pt]{article}
\usepackage[margin=2cm,columnsep=.5cm]{geometry}
\usepackage[greek,USenglish]{babel}
\usepackage[english]{isodate}
\languageattribute{greek}{ancient}% \usepackage[artemisia]{begingreek}  % https://ctan.math.illinois.edu/macros/latex/contrib/begingreek/begingreek.pdf
\usepackage{imakeidx}
%\usepackage[nopostdot,nogroupskip,nonumberlist]{glossaries-extra}
\usepackage[automake]{glossaries-extra}
\usepackage{enumitem}
\usepackage[normalem]{ulem}



\title{Vices of the New Testament}
\author{K. E. D. Paulsson}

\glsdisablehyper
\makeglossaries

\indexsetup{level=\section*,toclevel=section}
\makeindex[name=vicelist,title=Lists with Vices,columns=2]
\makeindex[name=eng,title=Vices in English,columns=2]
\makeindex[name=grc,title=Vices in Greek,columns=2]

\setcounter{secnumdepth}{0}


\def \tdntBertram {Bertram, Georg}
\def \tdntBauernfeind {Bauernfeind, Otto}
\def \tdntMichaelis {Michaelis, Wilhelm}
\def \tdntBeyer {Beyer, Hermann Wolfgang}
\def \tdntBehm {Behm, Johannes}
\def \tdntBietenhard {Bietenhard, Hans}
\def \tdntGrundmann {Grundmann, Walter}
\def \tdntBuchsel {Büchsel, Hermann Martin Friedrich}
\def \tdntConzelmann {Conzelmann, Hans Georg}
\def \tdntHanse{Hanse, Hermann}
\def \tdntFoerster{Foerster, Werner}
\def \tdntBultmann{Bultmann, Rudolf}
\def \tdntSchlier{Schlier, Heinrich}
\def \tdntPreisker{Preisker, Herbert}
\def \tdntHarder{Harder, Günther}
\def \tdntStrathmann{Strathmann, Hermann}
\def \tdntStumpff{Stumpff, Albrecht}
\def \tdntHauck{Hauck, Friedrich}
\def \tdntGutbrod{Gutbrod, Walter}
\def \tdntSchneider{Schneider, Johannes}
\def \tdntKleinknecht{Kleinknecht, Hermann Martin}
\def \tdntStahlin{Stählin, Gustav}
\def \tdntDelling{Delling, Gerhard}
\def \tdntRengstorf{Rengstorf, Karl Heinrich}
\def \tdntKittel{Kittel, Gerhard}
\def \tdntSchrenk{Schrenk, Gottlob}
\def \tdntGoppelt{Goppelt, Leonhard}

\begin{document}
\frenchspacing
\newcommand{\entlbl}[1]{\index[eng]{#1}\label{itm:#1}}
\newcommand{\entref}[1]{\emph{#1} ~($\rightarrow$~\pageref{itm:#1})}
\newcommand{\entrefgls}[1]{\emph{#1}$\rightarrow$\pageref{itm:#1}}
\newcommand{\grc}[1]{\greektext{#1}\latintext}
\newcommand{\cdfoot}[2]{\footnote{\emph{CD}, s.v. ``{#1},'' accessed \printdate{#2}.}}
\newcommand{\bkfoot}[3]{\footnote{{#3}, ``{#1},'' \emph{TDNT} {#2}.}}
\newcommand{\bksfoot}[2]{\footnote{{#2}, \emph{TDNT} {#1}.}}
%\newcommand{\cdfoot}[2]{\footnote{\emph{Cambridge Dictionary}, s.v. ``{#1},'' accessed \printdate{#2},\\https://dictionary.cambridge.org/dictionary/english/{#1}.}}


\newcommand{\entgls}[1]{\gls{#1} \glsdesc{#1}}
\newcommand{\entglos}[1]{\\\textbf{\gls{#1}} \glsdesc{#1}}



\maketitle

\input{section/abstract}

\section{Abbreviations}
\begin{description}
    \item[NA28] Novum Testamentum Graece, Nestle-Aland, 28th ed.
	\item[NT] The New Testament of the Bible.
	\item[OT] The Old Testament of the Bible.
	\item[BW10] BibleWorks 10 bible software with report tool.
	\item[BNM] BW10 Greek New Testament Morphology.
	\item[TDNT] Theological Dictionary of the New Testament (a.k.a. Big Kittels).
	\item[CD] Cambridge Dictionary accessed online from https://dictionary.cambridge.org/dictionary\\/english/\textlangle entry\textrangle.
	\item[EB] Encyclopedia Britannica accessed online from https://www.britannica.com/science/\textlangle article\textrangle.
\end{description}

\input{section/introduction}
\input{section/methodology}
\input{section/notice}

\section{Vice Entries}
\begin{description}[leftmargin=0pt]
  \input{entry/abhorrer}
  \input{entry/abomination}
  \input{entry/abortifacient}
  \input{entry/absurd_talk}
  \input{entry/abuser}
  \input{entry/adulterer}
  \input{entry/adultery}
  \input{entry/arrogance}
  \input{entry/avaricious}
  \input{entry/beguile}
  \input{entry/betrayer}
  \input{entry/bitterness}
  \input{entry/blasphemy_conduct}
  \input{entry/blasphemy_state}
  \input{entry/blood}
  \input{entry/brutal_violence}
  \input{entry/bully}
  \input{entry/calumniator}
  \input{entry/carouse}
  \input{entry/catamite_inconclusive}
  \input{entry/choked}
  \input{entry/clamor}
  \input{entry/common}
  \input{entry/contempt}
  \input{entry/covetousness}
  \input{entry/craving}
  \input{entry/deceiving}
  \input{entry/defamatory}
  \input{entry/demon_worship}
  \input{entry/depravity}
  \input{entry/depraved}
  \input{entry/devil}
  \input{entry/disinforming}
  \input{entry/disobedient_to_parents}
  \input{entry/disobedient}
  \input{entry/dissipated}
  \input{entry/disunity}
  \input{entry/drugs}
  \input{entry/drunkenness_woman}
  \input{entry/drunkenness}
  \input{entry/egomaniacal}
  \input{entry/egotist}
  \input{entry/enmity}
  \input{entry/ensnaring}
  \input{entry/erotic_perversion}
  \input{entry/evil}
  \input{entry/exterminator}
  \input{entry/extortionary}
  \input{entry/false_assertion}
  \input{entry/falsehood}
  \input{entry/fanaticism}
  \input{entry/father-murderer}
  \input{entry/festival}
  \input{entry/foolishness}
  \input{entry/forceful-interference}
  \input{entry/fraudster}
  \input{entry/fraud}
  \input{entry/gay-partner}
  \input{entry/god-hating_inconclusive}
  \input{entry/godless}
  \input{entry/gossipmonger}
  \input{entry/gossip}
  \input{entry/greed}
  \input{entry/hateful}
  \input{entry/haughty_disdain_conduct}
  \input{entry/haughty_disdain_state}
  \input{entry/hostility}
  \input{entry/hubris}
  \input{entry/husband-murderer}
  \input{entry/hypocrisy}
  \input{entry/idolater}
  \input{entry/idolatry}
  \input{entry/idol_meat}
  \input{entry/idol_pollution}
  \input{entry/idol_worship}
  \input{entry/impious}
  \input{entry/ill-will}
  \input{entry/injure}
  \input{entry/insolent}
  \input{entry/insult}
  \input{entry/irreconcilable}
  \input{entry/kidnapper}
  \input{entry/killing}
  \input{entry/lawless}
  \input{entry/liar}
  \input{entry/loving_pleasure_rather_than_loving_God}
  \input{entry/lunacy}
  \input{entry/machiavellian}
  \input{entry/magician}
  \input{entry/maleficent_contriver}
  \input{entry/maleficent_craving}
  \input{entry/maleficent_eye}
  \input{entry/male-prostitute}
  \input{entry/male-sex-buyer}
  \input{entry/malevolence}
  \input{entry/malice}
  \input{entry/miscomprehension}
  \input{entry/mockery}
  \input{entry/money-phile}
  \input{entry/mother-murderer}
  \input{entry/murderer}
  \input{entry/nests_multiple}
  \input{entry/oppressor}
  \input{entry/outburst}
  \input{entry/outcry}
  \input{entry/overindulgence}
  \input{entry/perjured}
  \input{entry/polygamy}
  \input{entry/potions}
  \input{entry/pretender}
  \input{entry/profane}
  \input{entry/prostitution}
  \input{entry/quarrel}
  \input{entry/rage}
  \input{entry/rape}
  \input{entry/rashness}
  \input{entry/rebellious}
  \input{entry/revel}
  \input{entry/revenge}
  \input{entry/rivalry}
  \input{entry/sectarianism}
  \input{entry/selfishness}
  \input{entry/selfish_triumph}
  \input{entry/self-seeking}
  \input{entry/sensuality}
  \input{entry/sexist_speech}
  \input{entry/sex-purchase}
  \input{entry/sexual-violation}
  \input{entry/shameful}
  \input{entry/shameful_gain}
  \input{entry/shameful_talk}
  \input{entry/sinner}
  \input{entry/slanderer}
  \input{entry/slander}
  \input{entry/spells}
  \input{entry/stealing_act_of}
  \input{entry/thief}
  \input{entry/timid}
  \input{entry/trafficker}
  \input{entry/unaffectionate}
  \input{entry/uncommitted}
  \input{entry/unfaithful}
  \input{entry/ungrateful}
  \input{entry/unmerciful}
  \input{entry/unrighteousness}
  \input{entry/unscrupulous_competition}
  \input{entry/unscrupulous_encroaching}
  \input{entry/uproar}
  \input{entry/vainglorious-arrogance}
  \input{entry/vicious}
  \input{entry/violence-rich-to-poor}
  \input{entry/wannabe}
  \input{entry/wine_abstinence}
  \input{entry/wine_alcoholic}
  \input{entry/wine_enslavement}
  \input{entry/wine_romp}
  \input{entry/witchbrew}
  \input{entry/witchcraft_use_of}
  \input{entry/wrath}
\end{description}

\input{section/congregational_protection}
\input{section/avoidance_exclusion}
\input{section/grace_exclusion}
\input{section/heavenly_exclusion}
\input{section/topic_depravement}
\input{section/topic_evil_spirits}
\input{section/topic_malice_evil}
\input{section/vices_of_eschatology}

\input{section/all_lists}
\input{section/vice_index}

\input{section/conclusion}

\section{Bibliography}
\begin{description}
	\item E. Nestle, K. Aland et al., \emph{Novum Testamentum Graece, twenty-eighth edition}. Stuttgart: Deutsche Bibelgesellschaft, 2012.
	\item Bushell, Michael S., Jean-Noel Aletti and Andrzej Gieniusz. \emph{BibleWorks Greek New Testament Morphology (BNM)}. 1999-2001. \emph{BibleWorks 10.0.8.755} BibleWorks, 2017.
	\item Kittel, Gerhard, and Gerhard Friedrich, eds. \emph{Theological Dictionary of the New Testament}. Translated by Geoffrey W. Bromiley. 10 vols. Grand Rapids: Eerdmans, 1964--1976.
	\item Henry George Liddell. Robert Scott.  \emph{A Greek-English Lexicon}. Revised and augmented throughout by Sir Henry Stuart Jones, with the assistance of Roderick McKenzie. Oxford: Clarendon Press, 1940.
	\item Thayer, Joseph Henry. \emph{Greek-English Lexicon of the New Testament}. 4th ed. Edinburgh: T. \& T. Clark, 1896.
	\item Lewis, Charlton T., and Charles Short. \emph{A Latin Dictionary}. Founded on Andrew's Edition of Freund's Latin Dictionary. LL.D. Oxford: Clarendon Press, 1879.
	\item \emph{Cambridge Dictionary}, 2023 years edition. (Internet). Cambridge: Cambridge University Press \& Assessment, 2023.\\ https://dictionary.cambridge.org/.
	\item \emph{Encyclopedia Britannica}, T. Editors of Encyclopaedia, 2023 years edition. (Internet). Chicago: Encyclopædia Britannica, Inc, 2023.\\https://www.britannica.com/.
	\item Loder, Charles. \emph{Greek Transliteration}. (Internet). 2022. \emph{greek-transliteration v2.0.0} Greek Transliteration, 2023. https://charlesloder.github.io\\/greekTransliteration/index.html
\end{description}

\section{Greek Antiquities}
\begin{description} % brutal (violence)
    \item Plato. \emph{Platonis Opera}. Edited by John Burnet. Oxford: Oxford University Press, 1903.
    \item Plato. \emph{Plato in Twelve Volumes}. Vols. 5 \& 6 translated by Paul Shorey. London: Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1969.

    \item Isaeus. \emph{Isaeus}. With an English translation by Edward Seymour Forster. London: M.A. Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1962.

    \item Demosthenes. \emph{Demosthenis.Orationes}. Edited by S. H. Butcher. Oxford: Clarendon Press, 1903.
    \item Demosthenes. \emph{Demosthenes}. With an English translation by J. H. Vince. London: M.A. Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1930.

    \item Demosthenes. \emph{Demosthenis.Orationes}. Edited by S. H. Butcher and W. Rennie. Oxonii: E Typographeo Clarendoniano, 1907 and 1921.
    \item Demosthenes. \emph{Demosthenes}. With an English translation by A. T. Murray, Ph.D. London: LL.D. Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1939.

    \item Andocides. \emph{Minor Attic Orators in two volumes 1, Antiphon Andocides}. With an English translation by K. J. Maidment. London: M.A. Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1968.
    \item Lysias. \emph{Lysias}. With an English translation by W.R.M. Lamb. London: M.A. Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1930.
\end{description}

\begin{description} % brutal (violence)
	\item Herodotus. \emph{Herodotus}. With an English translation by A. D. Godley. Cambridge: Harvard University Press, 1920.
	\item Aeschines. \emph{Aeschines}. With an English translation by Charles Darwin Adams. Ph.D. London: Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1919.
\end{description}

\begin{description} % revel
 	\item Plato.\emph{Plato in Twelve Volumes} Vol. 12 translated by Harold N. Fowler. London: Cambridge, MA, Harvard University Press; William Heinemann Ltd, 1921.
	\item Xenophon. \emph{Xenophontis opera omnia} vol. 4. Oxford: Clarendon Press, 1910 (repr. 1970).
	\item Xenophon. \emph{Xenophon in Seven Volumes} 5 and 6. Walter Miller. London: Harvard University Press, Cambridge, MA; William Heinemann, Ltd., 1914.
\end{description}

\onecolumn
% \printindex[vicelist]
% \printindex[eng]
%\printindex[grc]

\end{document}
