\section{Methodology}

When performing this study of vices, several approaches have been used
when trying to restore the true meaning of a certain Greek word or phrase.

The important thing is to be able to cite renowned works of other people,
historians, theologians, and so on. Because of this, only the most trustworthy
and recognized works have been consulted.

The most useful tool for effective studies has been the use of the bible software
BibleWorks version 10 (BW10) which has allowed systematic word and phrase studies with 
support for morphosyntax. This has enabled searches for words based on their 
lexeme in which the inflections have been tagged and made available in the search query.
 
Among others, Liddell \& Scott (LSJ) is used, mostly from BW10 but also accessed from the
Perseus Digital Library\footnote{PDL website, https://perseus.tufts.edu.}
 (PDL) website of Tufts University, for a deeper understanding. 
In some cases, it's clear that the  LSJ builtin module in BW10 has been selectively 
censored, especially sensitive words in the presumably sexual area.

The bible dictionaries known as Thayer's but also Gingrich and Danker's edition
of Bauer–Danker–Arndt–Gingrich (BDAG) have been used. Also, The Theological Dictionary 
of the New Testament (TDNT) is heavily consulted and also authoritative.

First, the word has been looked up in Liddell to get a secular understanding,
then this has been compared to with Thayer's, Gingrich and Danker's bible dictionaries. 
Sometimes this has been satisfactory but not always. In other cases, 
TDNT has been researched, which offers an extensive explanation of certain words and
phrases in all knowable aspects. If the TDNT has been satisfactory it is the only used source.

In some special cases, cognate studies have been made. This means that all
the similar words with their semantic values have been added up to get a
better view of the true meaning of a Greek word. In even rarer cases most
of the cited ancient Greek resources have been looked up in their ancient
Greek context -- referenced from LSJ hosted at PDL -- together with their 
respective English translation. Then the semantic value of those texts have been compiled 
into a specific understanding of a word that previously was vague in the bible dictionaries. 
The best example is the research done for the Greek word \grc{ἀσέλγεια}.

If the ancient Greek sources with their respective translations haven't produced
an interpretable result, then a word study has been performed in both LXX and NA28.

Hopefully, the methodology presented so far should have produced a result of 
entries over vices, of such good quality so that they may be used for further research
and also for practical use in Christianity, which is my goal and desire, to clean
up faulty chastisements that have hurt believers when the word of God has been
misinterpreted or used carelessly!
