\item[Witchcraft (use of),]
\entlbl{witchcraft} 

\grc{φαρμακεία}
\index[grc]{φαρμακεια@\grc{φαρμακεία}} 
(\textit{pharmakeia}):
\newglossaryentry{pharmakeia}
{
    name=\grc{φαρμακεία},
    description={i. \entrefgls{witchcraft} ii. \entrefgls{abortifacient} iii. \entrefgls{drugs} iv. \entrefgls{potions} v. \entrefgls{spells}},
    sort=φαρμακεια@\grc{φαρμακεία}
}
Thayer, Danker, and Gingrich agree with Liddell on the magick part of \grc{φαρμακεία}. 
Foremost \grc{φαρμακεία} means ``the use of \emph{drugs}, \emph{potions}, \emph{spells}, \ldots poisoning, \emph{witchcraft}, \ldots remedy, cure. [emphasis added]''
Further, ``use of \emph{drugs}, esp. of purgatives, \ldots emetics, Arist.Pr.962a3; of \emph{abortifacients}, \ldots generally, the use of any kind of \emph{drugs}, \emph{potions}, or \emph{spells}, \ldots poisoning or \emph{witchcraft}, \ldots metaph., remedy. [emphasis added]'' 
Then: examining the cognates found in L. gives a broader understanding of what the concept of \grc{φαρμα-} is, \grc{φαρμακάω} ``to suffer from the effect of poison, to be ill or distraught,'' \grc{φαρμακεύς} ``a poisoner, sorcerer,'' \grc{φαρμακεύω} ``to administer a drug, \ldots to use enchantments, \ldots to use it as a charm to calm the river, \ldots to drug, give him a poisonous or stupefying drug,'' \grc{φαρμακίς} ``a sorceress, witch,'' \grc{φάρμακον} ``a drug, medicine, \ldots medicine for it, remedy against it, \ldots for a head-ache, \ldots in bad sense, an enchanted potion, philtre, so a charm, spell, enchantment, \ldots also a drug, poison, \ldots a remedy, cure, \ldots of a bridle, \ldots a remedy against,'' \grc{φαρμακοποσία} ``drinking of medicine, \ldots drinking of poison,'' \grc{φαρμακοπώλης} ``a dealer in drugs,'' \grc{φαρμακοτρίβης} ``one who grinds drugs or colors,'' \grc{φαρμακόω} ``to endue with healing power,'' \grc{φαρμακώδης} ``of the nature of a \grc{φάρμακον}, medicinal, \ldots poisonous,'' \grc{φαρμάσσω} ``to treat by using \grc{φάρμακα}, \ldots to heal or relieve by medicine, \ldots to bewitch by potions or philtres: hence to bewitch by flattery.'' 
In the day and age of the Greeks, it was hard to tell the difference between magick and what counts as medicine in modern-day terms, and the concepts converged. In Gen 1:29, God gave herbs as food for humans and animals, which may work as remedies or cures. The focus is on the evil use, that is, the use of \emph{drugs} (not medicine), \emph{potions} (magical), the use of \emph{spells}, and \emph{abortifacients}, which sums up \emph{witchcraft}.
Found in Gal 5:20.
